---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# noder

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

`noder` provides helper functions to install node JS into a user-accessible directory (not a system installation), so that system `node` calls can then be made from within R.

## Installation

You can install from [GitHub](https://github.com/scienceuntangled/noder) with:

```{r eval = FALSE}
## install.packages("remotes") ## if needed
remotes::install_github("scienceuntangled/noder")

```

## Example usage

Install node. You only need to do this once.

```{r eval = FALSE}
library(noder)
nr_install_node()
```

The node executable should now be found:

```{r}
nr_node_exe()
```

You can then call that node executable using `system()` or similar commands. The `nr_exec_*` functions provide trivial wrappers around the `sys::exec_*` functions, passing the full path to node as the `cmd` argument to those functions:

```{r}
## equivalent to a system call of `node --version`
nr_exec_wait("--version")

```

Alternatively, add `node` to the system path with `nr_add_node_path()`, and then subsequent system calls should find `node` or `npm`:

```{r}
nr_add_node_path()
system2("node", "--version", stdout = TRUE)
system2("npm", "--version", stdout = TRUE)

```
